Results hyperparameter optimization

### 2020-04-09 simulation_study/hpoptimization/config/README.Rmd
update plots hyperopt

```{r, eval = FALSE}
php(hpsets$lr_doc2vec) + 
  labs(title = "Hyperparameters Logistic Regression + Doc2Vec")
```

@@

statistics for random forest + tf-idf
```{r}

hpsets$rf_tfidf %>%
   group_by(param, group) %>%
    summarise(variance = var(value), 
              sd = sd(value),
              min = min(value), 
              mean = mean(value),
              median = median(value),
              max = max(value)) %>%
  kable("markdown")

@@

>>>>

```{r, eval}
php(hpsets$lr_d2v) + 
  labs(title = "Hyperparameters Logistic Regression + Doc2Vec")
```

@@

@@

statistics for random forest + tf-idf
```{r}
hpsets$rf_tfidf %>%
   group_by(param, group) %>%
    summarise(variance = var(value), 
              sd = sd(value),
              min = min(value), 
              mean = mean(value),
              median = median(value),
              max = max(value)) %>%
  kable("markdown")
```
